Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1) \note{\scriptsize Authors, please add/check middle initials and affiliations}

### 2014-04-15 WSSSPE1_report/WSSSPE1_summary_report.tex
Fix typo in a name

\author{Daniel~S.~Katz$^{(1)}$,
Sou-Cheng~T.~Choi$^{(2)}$,
Hilmar~Lapp$^{(3)}$,
Ketan~Maheshwari$^{(4)}$,
Frank~L\:{o}ffler$^{(5)}$, 
Matthew~Turk$^{(6)}$,
Marcus~D.~Hanwell$^{(7)}$,
Nancy~Wilkins-Diehr$^{(8)}$,
James~Hetherington$^{(9)}$, 
James~Howison$^{(10)}$,
Shel~Swenson$^{(11)}$, 
Gabrielle~D.~Allen$^{(12)}$,
Bruce~Berriman$^{(13)}$,
Andy~R.~Terrel$^{(14)}$,
Colin~Venters$^{(15)}$
}

>>>>

\author{Daniel~S.~Katz$^{(1)}$,
Sou-Cheng~T.~Choi$^{(2)}$,
Hilmar~Lapp$^{(3)}$,
Ketan~Maheshwari$^{(4)}$,
Frank~Löffler$^{(5)}$, 
Matthew~Turk$^{(6)}$,
Marcus~D.~Hanwell$^{(7)}$,
Nancy~Wilkins-Diehr$^{(8)}$,
James~Hetherington$^{(9)}$, 
James~Howison$^{(10)}$,
Shel~Swenson$^{(11)}$, 
Gabrielle~D.~Allen$^{(12)}$,
Bruce~Berriman$^{(13)}$,
Andy~R.~Terrel$^{(14)}$,
Colin~Venters$^{(15)}$
}
